---
title: "Aqauculture Deep Dive"
author: 'By: Claire Gonzales'
date: '2022-08-16'
output: 
  html_document: 
    theme: lumen
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(tidyselect)
library(here)
library(ggbeeswarm)
library(dplyr)
library(rstatix)

```


```{r}
mydata <- read_csv(here("data", "Data_total_working_for_r.csv"))
  
```

```{r}
aquaculture <- mydata %>% 
  select(id, year, aquaculture_present, ecology, governance, socioecon) %>% 
  filter(aquaculture_present == "1")

aqua_mini <- aquaculture %>% 
  group_by(aquaculture_present) %>% 
  summarize(
    eco = sum(ecology),
    gov = sum(governance),
    socio = sum(socioecon)
  )
  
```

```{r}
wind <- mydata %>% 
  select(id, year, wind_present, ecology, governance, socioecon) %>% 
  filter(wind_present == "1")

wind_mini <- wind %>% 
  group_by(wind_present) %>% 
  summarize(
    eco = sum(ecology),
    gov = sum(governance),
    socio = sum(socioecon)
  )
```

```{r}
max_depth_m <- as.numeric(c(25, 16, 33.4, 40, 200, 500, 70, 40, 300, 60, 40, 200, 300, 200))

median(max_depth_m)

```

```{r}
distance_km <- as.numeric(c(15, 16, 55, 10, 30, 8, 1.2, 1.9, 37, 60, 22, 16, 32, 25))

median(distance_km)
```

```{r}
sigwaveheight_m <- as.numeric(c(1.5, 1.25, 2.1, 2, 2, 1.8, 5))

median(sigwaveheight_m)
```

## Incorporating metrics 
Looking into aquaculture metrics
```{r}
aqdata <- read.csv(here("data", "Data_total_working_for_r_aq.csv"))
```

```{r}
aqdata_sub <- aqdata %>% 
  filter(metric == "Aquaculture") %>% 
  select("metric", "id", "title", "distance_to_shore", "depth_min", "depth_max", "depth_ave", "wave_height_average_m", "sst_c", "chla") 
  
aqdata_sub_2 <- aqdata %>% 
  filter(metric == "Aquaculture") %>% 
  select("metric", "id", "title", "distance_to_shore", "depth_min", "depth_max", "depth_ave", "wave_height_average_m", "sst_c", "chla", "wind_present", "wave_present", "tidal_present", "other_present") 
  
  
  # summarize(dist_median = median(distance_to_shore, na.rm = TRUE),
  #           depth_max_median = median(depth_max, na.rm = TRUE),
  #           sigwave_median = median(wave_height_average_m, na.rm = TRUE),
  #           sst_median = median(sst_c, na.rm = TRUE),
  #           chla_median = median(chla, na.rm = TRUE))
```

Looking at wind metrics
```{r}
winddata <- read.csv(here("data", "Data_total_working_for_r_wind.csv"))
```

```{r}
winddata_sub <- winddata %>% 
  filter(metric == "Wind") %>% 
  select("metric", "id", "title", "distance_to_shore", "depth_min", "depth_max", "depth_ave", "wave_height_average_m", "sst_c", "chla") 


  # group_by(metric) %>% 
  # summarize(dist_median = median(distance_to_shore, na.rm = TRUE),
  #           depth_max_median = median(depth_max, na.rm = TRUE),
  #           sigwave_median = median(wave_height_average_m, na.rm = TRUE),
  #           sst_median = median(sst_c, na.rm = TRUE),
  #           chla_median = median(chla, na.rm = TRUE))
```

```{r}
wavedata <- read.csv(here("data", "Data_total_working_for_r_wave.csv"))
```

```{r}
wavedata_sub <- wavedata %>% 
  filter(metric == "Wave") %>% 
  select("metric", "id", "title", "distance_to_shore", "depth_min", "depth_max", "depth_ave", "wave_height_average_m", "sst_c", "chla")
```


```{r}
datadata <- rbind(aqdata_sub, winddata_sub, wavedata_sub)
```


Comparing distances to shore across discipline

```{r}
ggplot(data = datadata, aes(x = metric, y = distance_to_shore)) +
  geom_beeswarm(aes(color = metric)) +
  scale_color_manual(values = c("goldenrod2","cyan4","coral")) +
  geom_boxplot(fill = NA, width = 0.3, outlier.color = NA) +
  stat_summary(fun=median, 
               geom="point", 
               shape=20, 
               size=3, 
               color="black", 
               fill="black") +
  labs(x = "Ocean activity",
       y = "Distance from shore (m)") +
  theme_minimal() +
  theme(legend.title = element_blank())

```

**Figure 4.** Shows the distances from shore (meters) across the three most common ocean activities listed in co-location literature. Metrics withing aquaculture (n = ), wave energy (n = ), and wind energy (n = ) all reflect  similar distances from shore. Significance across these three data groups was checked using a Kruskal-Wallis test (p = 0.394).

Comparing maximum listed depths across discipline
```{r}
ggplot(data = datadata, aes(x = metric, y = depth_ave)) +
  geom_beeswarm(aes(color = metric)) +
  scale_color_manual(values = c("goldenrod2","cyan4","coral")) +
  geom_boxplot(fill = NA, width = 0.3, outlier.color = NA) +
  stat_summary(fun=median, 
               geom="point", 
               shape=20, 
               size=3, 
               color="black", 
               fill="black") +
    labs(x = "Ocean Activity",
         y = "Average Depth (m)") +
  theme_minimal() +
  theme(legend.title = element_blank())
```

**Figure 5.** Shows the average depth (meters) across the three most common ocean activities listed in co-location literature. Metrics withing aquaculture (n = ), wave energy (n = ), and wind energy (n = ) all reflect  similar distances from shore. Significance across these three data groups was checked using a Kruskal-Wallis test (p = 0.551). 


Comparing minimum listed depths across discipline
```{r, include=FALSE, eval=FALSE}
ggplot(data = datadata, aes(x = metric, y = depth_min)) +
  geom_beeswarm(aes(color = metric)) +
  scale_color_manual(values = c("goldenrod2","cyan4","coral")) +
  geom_boxplot(fill = NA, width = 0.3, outlier.color = NA) +
  stat_summary(fun=median, 
               geom="point", 
               shape=20, 
               size=3, 
               color="black", 
               fill="black") +
  theme_minimal()
```

Comparing maximum listed significant wave heights across discipline
```{r}
ggplot(data = datadata, aes(x = metric, y = wave_height_average_m)) +
  geom_beeswarm(aes(color = metric)) +
  scale_color_manual(values = c("goldenrod2","cyan4","coral")) +
  geom_boxplot(fill = NA, width = 0.3, outlier.color = NA) +
  stat_summary(fun=median, 
               geom="point", 
               shape=20, 
               size=3, 
               color="black", 
               fill="black") +
  theme_minimal()
```

Comparing SSTs (degrees celcius) across disciplines
```{r}
ggplot(data = datadata, aes(x = metric, y = sst_c)) +
  geom_beeswarm(aes(color = metric)) +
  scale_color_manual(values = c("goldenrod2","cyan4","coral")) +
  geom_boxplot(fill = NA, width = 0.3, outlier.color = NA) +
  stat_summary(fun=median, 
               geom="point", 
               shape=20, 
               size=3, 
               color="black", 
               fill="black") +
  theme_minimal()
```

## ANOVA of aquaculture metrics

Comparing aquaculture metrics against wind and wave
```{r}
datadata_anova <- aov(depth_ave ~ metric, data = datadata)

summary(datadata_anova)

# depth_ave: p-value = 0.551
# distance to shore: p-value = 0.394

```

Making the same comparison using a Kruskal-Wallis test.
```{r}
datadata_kruswall <- kruskal.test(depth_ave ~ metric, data = datadata)

datadata_kruswall

# depth_ave: p-value = 0.4673
# distance to shore: p-value = 0.3366
```
Kruskal Wallis test is the better test for this data because we violate the assumtions of the ANOVA, but a Kruskal Wallis test does not require these assumptions. Kruskal Wallis is non-parametric and ranks-based assessment of medians 

### Sample sizes
Determining the n values of distance from shore and average depth for each ocean activity in datadata

summary_datadata has the median values
nvals_datadata has the n values
```{r}
summary_datadata <- datadata %>% 
  group_by(metric) %>% 
  summarize(median_depth = median(depth_ave, na.rm = TRUE),
            median_dist = median(distance_to_shore, na.rm = TRUE))


nvals_datadata_depth <- datadata %>% 
  filter(depth_ave != "NA") %>% 
  group_by(metric) %>% 
  summarize(n_depth = n())

nvals_datadata_dist <- datadata %>% 
  filter(distance_to_shore != "NA") %>% 
  group_by(metric) %>% 
  summarize(n_dist = n()) %>% 
  rename(metric_dist = metric) #renaming because r was getting confused by 2 columns with same name in cbind()

nvals_datadata <- as_tibble(cbind(nvals_datadata_depth, nvals_datadata_dist)) %>% 
  select("metric", "n_depth", "n_dist")
              
```


### Depth of Aquaculture Projects

```{r}
aqua_wind <- aqdata_sub_2 %>% 
  filter(wind_present == "1") %>% 
  mutate(buddy = rep("wind", 16))
```

```{r}
aqua_wave <- aqdata_sub_2 %>% 
  filter(wave_present == "1") %>% 
  mutate(buddy = rep("wave", 4))

```

```{r}
aqua_tidal <- aqdata_sub_2 %>% 
  filter(tidal_present == "1") %>% 
  mutate(buddy = rep("tidal", 2))


```

```{r}
aqua_other <- aqdata_sub_2 %>% 
  filter(other_present == "1") %>% 
  mutate(buddy = rep("other", 7))


```

```{r}
alltogether <- as_tibble(rbind(aqua_wind, aqua_wave, aqua_tidal, aqua_other))
```


Graphing the depth differences of aquaculture at different depths
```{r}
ggplot(data = alltogether, aes(x = metric, y = depth_ave)) +
  geom_jitter(aes(color = buddy)) +
  scale_color_manual(values = c("goldenrod2","cyan4","coral", "darkviolet")) +
  geom_boxplot(fill = NA, width = 0.3, outlier.color = NA) +
  stat_summary(fun=median,
               geom="point",
               shape=20,
               size=4,
               color="black",
               fill="black") +
  theme_minimal() +
  scale_y_reverse()
```


```{r}
ggplot(data = alltogether, aes(x = buddy, y = depth_ave)) +
  geom_beeswarm(aes(color = buddy)) +
  scale_color_manual(values = c("goldenrod2","cyan4","coral", "darkviolet")) +
  geom_boxplot(fill = NA, width = 0.3, outlier.color = NA) +
  stat_summary(fun=median,
               geom="point",
               shape=20,
               size=3,
               color="black",
               fill="black") +
  theme_minimal() +
  scale_y_reverse()
```

Graphing the depth differences of aquaculture at different distances from shore
```{r}
ggplot(data = alltogether, aes(x = metric, y = distance_to_shore)) +
  geom_jitter(aes(color = buddy)) +
  scale_color_manual(values = c("goldenrod2","cyan4","coral", "darkviolet")) +
  geom_boxplot(fill = NA, width = 0.3, outlier.color = NA) +
  stat_summary(fun=median, 
               geom="point", 
               shape=20, 
               size=4, 
               color="black", 
               fill="black") +
  theme_minimal()
```

```{r}
ggplot(data = alltogether, aes(x = buddy, y = distance_to_shore)) +
  geom_beeswarm(aes(color = buddy)) +
  scale_color_manual(values = c("goldenrod2","cyan4","coral", "darkviolet")) +
  geom_boxplot(fill = NA, width = 0.3, outlier.color = NA) +
  stat_summary(fun=median, 
               geom="point", 
               shape=20, 
               size=3, 
               color="black", 
               fill="black") +
  theme_minimal()
```

## aquaculture depths with no duplicates

```{r}
ggplot(data = aqdata_sub_2, aes(x = metric, y = depth_ave)) +
  geom_jitter(aes(color = metric)) +
  # scale_color_manual(values = c("goldenrod2","cyan4","coral", "darkviolet")) +
  geom_boxplot(fill = NA, width = 0.3, outlier.color = NA) +
  stat_summary(fun=median,
               geom="point",
               shape=20,
               size=3,
               color="black",
               fill="black") +
  theme_minimal() +
  scale_y_reverse()
```

